---
title: "Exploring Penguin Body Mass with R"
author: "Weizhuo Zhang"
date: 2026-09-21
---

## Data Source

The data comes from the [Palmer Penguins dataset](https://allisonhorst.github.io/palmerpenguins/), collected and made available by Dr. Kristen Gorman and the Palmer Station Long Term Ecological Research (LTER) Program. The data is available under a [CC0 license](https://creativecommons.org/publicdomain/zero/1.0/).

```{r}
#| message: false
#| warning: false

library(palmerpenguins)
library(dplyr)
library(ggplot2)
```

## Data Cleaning

Clean the data before doing analysis

```{r}
penguins_clean <- penguins |>
  filter(!is.na(species), !is.na(body_mass_g))

head(penguins_clean)
```

## Species Calculation 

Calculate the body mass for each species

```{r}
penguins |>
  group_by(species) |>
  summarise(mean_body_mass_g = mean(body_mass_g, na.rm = TRUE))
```

## Figure of Body mass by species

Apply the figure to show the comparison of body mass from different species

```{r}
#| label: fig-penguin-mass
#| fig-cap: "Body mass of penguins by species."

ggplot(penguins_clean, aes(x = species, y = body_mass_g)) +
  geom_boxplot() +
  labs(x = "Species", y = "Body mass (g)")
```

The fgiure shows the body mass distribution of three penguin species. From the figure, we can see that Adelie and Chinstrap have similar range of body masses, while Gentoo has a much higher overall distribution than the former two species. 



